Comparison of dimensionality reduction schemes for parallel global optimization algorithms \thanks{The study was supported by the Russian Science Foundation, project No 16-11-10150}

### 2018-04-08 2018/RSD/MultiEvolvents/RSD.tex
RSD: tiny fixes

This allows problems to be solved in which function values may not be determined for the entire search domain. Under this approach, solving multidimen-sional problems is reduced (using Peano-type space-filling curves) to solving equivalent one-dimensional problems.
It should be noted that standard approaches to algorithm parallelization are not quite applicable to global optimization. For example, the rules for selecting an-other iteration point are quite simple and do not require parallelization (as over-heads associated with organizing parallel computations will nullify any possible acceleration). Some acceleration can be achieved by parallelizing the computa-tion of function values describing the object to be optimized; however, this ap-proach is specific to each individual problem being solved.
The following approach looks more promising. The algorithm can be modified to run several trials in parallel. This approach provides the efficiency (as paral-lelization is applied to the most computation-intensive part of the problem solv-ing process) and generality (in that it applies to a wide range of global optimiza-tion algorithms). The approach, described in  \cite{Two_Level_Parallel} for unconstrained optimization, was used in this work for parallelizing constrained optimization algorithms.

@@

%------------------------------------------------------------------------------
\section{Methods of Dimension Reduction}
\subsection{Базовый алгоритм}

@@

%------------------------------------------------------------------------------
\subsection{Сдвиговые}
\label{sec:shifted}

@@

%------------------------------------------------------------------------------
\subsection{Вращаемые}
The application of the scheme for building the multiple evolvents (hereinafter called the shifted evolvents or $S$-evolvents) described in Subsection \ref{sec:shifted} allows to preserve the information on the nearness of the points in the multidimensional space and, therefore, to provide more precise (as compared to a single evolvent) estimate of Lipschitz constant in the search process. However, this approach has serious restrictions, which narrow the applicability of the parallel algorithms, designed on the base of the $S$-evolvents.

>>>>

This allows problems to be solved in which function values may not be determined for the entire search domain. Under this approach, solving multidimensional problems is reduced (using Peano-type spacefilling curves) to solving equivalent one-dimensional problems.
It should be noted that standard approaches to algorithm parallelization are not quite applicable to global optimization. For example, the rules for selecting another iteration point are quite simple and do not require parallelization (as overheads associated with organizing parallel computations will nullify any possible acceleration). Some acceleration can be achieved by parallelizing the computa-tion of function values describing the object to be optimized; however, this approach is specific to each individual problem being solved.
The following approach looks more promising. The algorithm can be modified to run several trials in parallel. This approach provides the efficiency (as parallelization is applied to the most computation-intensive part of the problem solving process) and generality (in that it applies to a wide range of global optimiza-tion algorithms). The approach, described in  \cite{Two_Level_Parallel} for unconstrained optimization, was used in this work for parallelizing constrained optimization algorithms.

@@

%------------------------------------------------------------------------------
\section{Methods of Dimension Reduction}
\subsection{Single evolvent}

@@

%------------------------------------------------------------------------------
\subsection{Shifted evolvents}
\label{sec:shifted}

@@

%------------------------------------------------------------------------------
\subsection{Rotated evolvents}
The application of the scheme for building the multiple evolvents (hereinafter called the shifted evolvents or $S$-evolvents) described in Subsection \ref{sec:shifted} allows to preserve the information on the nearness of the points in the multidimensional space and, therefore, to provide more precise (as compared to a single evolvent) estimate of Lipschitz constant in the search process. However, this approach has serious restrictions, which narrow the applicability of the parallel algorithms, designed on the base of the $S$-evolvents.
